---
title: "Creating, updating & maintaining the bioacousticsquotes data base"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating, updating & maintaining the bioacousticsquotes data base}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bioacousticsquotes)
```

## Fformat for quotes file

The quotes are stored in the `data-raw/quotes_raw.txt` file. The script `data-raw/convert_quotes_to_rda.R` can be used to read these quotes and save them to `data/quotes.rda`, which is the main data file used in the package.

The `quotes_raw.txt` file uses the following format for each quotation.  Lines beginning with "%" are comments and ignored.  Other lines contain a "key:value" pair. The key is used to identify the right column when building the `quotes` data.frame:

```
% Comment
quo: This is a quotation.
src: Person or persons who said or wrote the quote.
cit: Citation for the original quote.
url: URL where the quote can be found (such as journal articles).
tag: Comma-separated tags to categorize the quote.
```

Here is an example:

```
quo: A judicious man looks at Statistics, not to get knowledge, but to save himself from having ignorance foisted on him.
src: Thomas Carlyle
cit: Chartism, 1840, Chapter II, Statistics
url: https://en.wikisource.org/wiki/Chartism/Chapter_2
tag: data visualization
```
